---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = 'man/figures/README-')
```

## Overview

This repo provides replication code for the book ["Casual Inference: The 
Mixtape"](http://scunning.com/stata.html) by Scott Cunningham.

## Chapters

- [Properties of regression](https://github.com/johnson-shuffle/mixtape-code/tree/master/ch03)

- [Directed acyclical graphs](https://github.com/johnson-shuffle/mixtape-code/tree/master/ch04)

- [Potential outcomes causal model](https://github.com/johnson-shuffle/mixtape-code/tree/master/ch05)

- [Matching and subclassification](https://github.com/johnson-shuffle/mixtape-code/tree/master/ch06)

- [Regression discontinuity](https://github.com/johnson-shuffle/mixtape-code/tree/master/ch07)

- Instrumental variables

- Panel data

- Differences-in-differences

- Synthetic control

## Packages

Most of the code relies on the following packages; note these are not explicitly loaded in the code chunks.

```{r packs, eval = F}
# tidyverse and tidyverse-adjacent
library(magrittr)
library(hms)
library(stringr)
library(lubridate)
library(forcats)
library(feather)
library(haven)
library(httr)
library(jsonlite)
library(readxl)
library(xml2)
library(rvest)
library(modelr)
library(broom)
library(blob)
library(dbplyr)
library(purrrlyr)
library(tidyverse)

# summary statistics
library(skimr)

# datasets
library(mixtape)

# figure styling
library(hrbrthemes)

# table styling
library(stargazer)
```
